# fredr
```{r setup, include=FALSE}
packrat::with_extlib("knitr",
                     opts_chunk$set(fig.width = 7,
                                    fig.height = 5,
                                    collapse = TRUE,
                                    comment = "#>"))
devtools::load_all()
options(digits = 4)
```
[![Travis
branch](https://img.shields.io/travis/sboysel/fredr/master.svg?style=flat-square)](https://travis-ci.org/sboysel/fredr)
[![Codecov](https://img.shields.io/codecov/c/github/sboysel/fredr/master.svg?style=flat-square)](https://codecov.io/github/sboysel/fredr)
[![GitHub
release](https://img.shields.io/github/release/sboysel/fredr.svg?style=flat-square)](https://github.com/sboysel/fredr/releases)
[![GitHub
license](https://img.shields.io/github/license/sboysel/fredr.svg?style=flat-square)](https://opensource.org/licenses/MIT)

`fredr` seamlessly interacts with the RESTful API for [Federal Reserve Economic
Data (FRED)](https://research.stlouisfed.org/fred2/), provided by the Federal
Reserve Bank of St. Louis.  Essentially a simple wrapper of
[`httr`](https://github.com/hadley/httr),
[`dplyr`](https://github.com/hadley/dplyr), and the FRED API itself, `fredr` is
designed with simplicity and flexibility in mind.  In addition a generic query
function `fredr` to return any query as a `tbl_df`, the package also provides
convenience functions `fredr_search` and `fredr_series` to simplify the process
to finding and importing FRED series as `R` objects.  As nearly all optional
parameters supplied to these functions are relayed verbatim to the API, the 
user is strongly encouraged to read the full [FRED
API](https://research.stlouisfed.org/docs/api/fred/) to leverage the full power
of the FRED API and `fredr`. The convenience function `api_docs` quickly brings
up the web documentation. See the [section below](#api_docs) for usage
examples.
## Installation
```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("sboysel/fredr")
```
## Quickstart
Load `fredr`
```{r load_libi, eval=FALSE}
library(fredr)
```
Set FRED API key in working directory.  You must first [obtain a FRED API
key](https://research.stlouisfed.org/docs/api/api_key.html).  It is also
recommended to reveiw the [FRED API Terms of
Use](https://research.stlouisfed.org/docs/api/terms_of_use.html).
```{r set_api_key, eval=FALSE}
set_api_key("abcdefghijklmnopqrstuvwxyz123456")
```
Search for FRED series
```{r fredr_search, message=FALSE, warning=FALSE}
fredr_search(search_text = "housing")
```
Get a FRED series.  Returns a `ts` object.
```{r fredr_series1, message=FALSE, warning=FALSE}
fredr_series(series_id = "HOUST",
             observation_start = "1990-01-01",
             observation_end = "1995-01-01")
```
Leverage the native features of the FRED API
```{r fredr_series2, message=FALSE, warning=FALSE}
fredr_series(series_id = "UNRATE",
             observation_start = "1990-01-01",
             frequency = "q",
             units = "chg")
```
Combine with other packages for a slick workflow
```{r fredr_series3, message=FALSE, warning=FALSE}
library(dplyr)
library(ggfortify)
fredr_series(series_id = "GNPCA",
             units = "log") %>%
  autoplot()
```
```{r fredr_series4, message=FALSE, warning=FALSE}
fredr_series(series_id = "GNPCA",
             units = "log") %>%
  diff() %>%
  autoplot()
```
```{r fredr_series5, message=FALSE, warning=FALSE}
fredr_series(series_id = "GNPCA",
             units = "log") %>%
  diff() %>%
  StructTS() %>%
  residuals() %>%
  acf(., main = "ACF for First Differenced real US GNP, log")
```
```{r fredr_series6, message=FALSE, warning=FALSE}
fredr_search(search_text = "federal funds",
             order_by = "popularity") %>%
  slice(1) %>%
  fredr_series(series_id = .$id) %>%
  window(., start = 2000, end = c(2000, 120))
```

Quickly access the FRED API web documentation for any endpoint
```{r api_docs, message=FALSE, warning=FALSE, eval=FALSE}
api_docs(endpoint = "series/observations")
```
You may also use the `params` option for `api_docs` to go straight to the
endpoint's Parameters section.
```{r api_docs2, message=FALSE, warning=FALSE, eval=FALSE}
api_docs(endpoint = "category/related_tags", params = TRUE)
```
You can also use the backbone function `fredr` to run more general queries
against *any* [FRED API
endpoint](https://research.stlouisfed.org/docs/api/fred/) (e.g. Categories,
Series, Sources, Releases, Tags).  This is also useful to return any arbitrary
information as a `tbl_df` object.
```{r fredr_general}
fredr(endpoint = "tags/series", tag_names = "population;south africa")
```
## See Also
The primary goal in creating `fredr` was educational.  I also suggest you check
out several other `R` packages designed for the FRED API:

* [jcizel/FredR](https://github.com/jcizel/FredR)
* [johnlaing/rfred](https://github.com/johnlaing/rfred)
* [jdvermeire/rfred](https://github.com/jdvermeire/rfred)


