# fredr
```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(fig.width = 7,
               fig.height = 5,
               collapse = TRUE,
               comment = "#>")
```
[![Travis
branch](https://img.shields.io/travis/sboysel/fredr/master.svg?style=flat-square)](https://travis-ci.org/sboysel/fredr)
[![AppVeyor Build Status](https://ci.appveyor.com/project/sboysel/fredr/branch/master)](https://ci.appveyor.com/project/sboysel/fredr/branch/master)
[![Codecov](https://img.shields.io/codecov/c/github/sboysel/fredr/master.svg?style=flat-square)](https://codecov.io/github/sboysel/fredr)
[![GitHub
release](https://img.shields.io/github/release/sboysel/fredr.svg?style=flat-square)](https://github.com/sboysel/fredr/releases)
[![GitHub
license](https://img.shields.io/github/license/sboysel/fredr.svg?style=flat-square)](https://opensource.org/licenses/MIT)

`fredr` interacts with the [Federal Reserve Economic
Data (FRED)](https://research.stlouisfed.org/fred2/) RESTful API, provided by the Federal
Reserve Bank of St. Louis.  Essentially a simple wrapper of
[`httr`](https://github.com/r-lib/httr) and the FRED API itself, `fredr` is
designed with simplicity and flexibility in mind.  The core functions are

- `fredr_series` - Fetch a FRED series.
- `fredr_search` - Search for a FRED series.
- `fredr` - Send a general request to the FRED API.

All objects are returned as `tibbles`.  As nearly all optional
parameters supplied to these functions are relayed verbatim to the API, the 
user is strongly encouraged to read the full [FRED
API](https://research.stlouisfed.org/docs/api/fred/) documentation to leverage the full power
of the FRED API and `fredr`.

## Installation

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("sboysel/fredr")
```

## Usage

See the [Getting started](http://sboysel.github.io/fredr/articles/fredr.html) article.

## See Also
The primary goal in creating `fredr` was educational.  I also suggest you check
out several other `R` packages designed for the FRED API:

* [business-science/tidyquant](https://github.com/business-science/tidyquant)
* [jcizel/FredR](https://github.com/jcizel/FredR)
* [joshuaulrich/quantmod](https://github.com/joshuaulrich/quantmod)
* [quandl/quandl-r](https://github.com/quandl/quandl-r)
* [johnlaing/rfred](https://github.com/johnlaing/rfred)
* [jdvermeire/rfred](https://github.com/jdvermeire/rfred)


