---
title: "Getting started with fredr"
author: "Sam Boysel"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Getting started with fredr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  eval = !(Sys.getenv("FRED_API_KEY") == ""),
  cache = TRUE,
  collapse = TRUE,
  comment = "#>"
)
library(fredr)
options(digits = 4)
```

# Introduction

`fredr` provides a complete set of `R` bindings to the [Federal Reserve Economic
Data (FRED)](https://research.stlouisfed.org/fred2/) RESTful API for, provided by 
the Federal Reserve Bank of St. Louis.  The functions allow the user to search 
for and fetch time series observations and associated metadata within the FRED 
database.  The core functions are

- `fredr_set_key()` - Set the required FRED API key for the session.
- `fredr()` or `fredr_series_observations()` - Fetch a FRED series.
- `fredr_series_search_text()` - Search for a FRED series by text.
- `fredr_request()` - Send a general request to the FRED API.

Objects are returned as `tibbles`.  The user is strongly encouraged to read the 
full [FRED API](https://research.stlouisfed.org/docs/api/fred/) documentation to 
leverage the full power of `fredr` and the FRED API.

## Installation

Currently, `fredr` is only available from GithHub.  You can install using `devtools::install_github`:

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("sboysel/fredr")
```

Load package

```{r fredr_load, eval=FALSE}
library(fredr)
```

## Authentication

To use `fredr` and the FRED API in general, you must first [obtain a FRED API
key](https://research.stlouisfed.org/docs/api/api_key.html).  It is also
recommended to reveiw the [FRED API Terms of
Use](https://research.stlouisfed.org/docs/api/terms_of_use.html).  Once you've obtained an API key, you can set the key as an environment variable using `fredr_set_key`

```{r fredr_set_key, eval=FALSE}
fredr_set_key("abcdefghijklmnopqrstuvwxyz123456")
```

where "abcdefghijklmnopqrstuvwxyz123456" is replaced with the actual key you obtain from FRED.  This will set the key for the current session.  You can persistently set the key by appending the line `FRED_API_KEY=abcdefghijklmnopqrstuvwxyz123456` to an `.Renviron` file in the working directory.  This can be done using a text editor or by running `usethis::edit_r_environ`.  If you edit the `.Renviron` file, remember to either restart the session or run `readRenviron(".Renviron")` for the changes to take effect. 

## Retrieve series observations

The `fredr()` function (an alias for `fredr_series_observations()`) retrieves series observations (i.e. the actual time series data) for a specified FRED series ID.  The function returns a `tibble` with 2 columns (observation date and value).

```{r fredr_series_observations, message=FALSE, warning=FALSE}
fredr(
  series_id = "UNRATE",
  observation_start = as.Date("1990-01-01")
)
```

Leverage the native features of the FRED API by passing additional parameters:

```{r fredr_series_observations2, message=FALSE, warning=FALSE}
fredr_series_observations(
  series_id = "UNRATE",
  observation_start = as.Date("1990-01-01"),
  frequency = "q",
  units = "chg"
)
```

`fredr` plays nicely with the [tidyverse](https://www.tidyverse.org/):

```{r fredr_series_observations3, message=FALSE, warning=FALSE}
library(tidyverse)
fredr_series_search_text(
  search_text = "federal funds",
  order_by = "popularity",
  sort_order = "desc",
  limit = 1) %>%
  pull(id) %>%
  fredr_series_observations(series_id = .) %>%
  ggplot(data = ., mapping = aes(x = date, y = FEDFUNDS)) +
    geom_line()
```

It is relatively straightforward to convert `tibbles` returned by `fredr` into other time series objects.  For example,

```{r fredr_series_observations4, message=FALSE, warning=FALSE}
library(xts)
gnpca <- fredr_series_observations(series_id = "GNPCA", units = "log") %>%
  mutate(GNPCA = GNPCA - lag(GNPCA)) %>%
  filter(!is.na(GNPCA))

gnpca_xts <- xts::xts(
  x = gnpca$GNPCA,
  order.by = gnpca$date
)

gnpca_xts %>%
  StructTS() %>%
  residuals() %>%
  acf(., main = "ACF for First Differenced real US GNP, log")
```

## Endpoints

`fredr` implements functions for all FRED API endpoints.  For usage examples for these functions, please consult the relevant vignette:

- [Categories](http://sboysel.github.io/fredr/articles/fredr-categories.html)
- [Releases](http://sboysel.github.io/fredr/articles/fredr-releases.html)
- [Series](http://sboysel.github.io/fredr/articles/fredr-series.html)
- [Sources](http://sboysel.github.io/fredr/articles/fredr-sources.html)
- [Tags](http://sboysel.github.io/fredr/articles/fredr-tags.html)

Finally, `fredr` is packaged with a list of possible endpoints in the `tibble` named `fredr_endpoints`:

```{r fredr_endpoints1, width = 180}
fredr_endpoints
```

## View FRED API documentation

To get the most out of the native features of the FRED API, it is highly recommended to review the [API endpoint documentation](https://research.stlouisfed.org/docs/api/fred/). Within an R session, you can quickly access the web documentation for any endpoint with the convenience function `fredr_docs`.  The following example will open a web browser to the FRED API documentation page on `series/observation` endpoint.

```{r fredr_docs1, message=FALSE, warning=FALSE, eval=FALSE}
fredr_docs(endpoint = "series/observations")
```

You may also use the `params` option for `fredr_docs` to go straight to the
endpoint's Parameters section.
```{r fredr_docs2, message=FALSE, warning=FALSE, eval=FALSE}
fredr_docs(endpoint = "category/related_tags", params = TRUE)
```

## General queries

You can also use the low-level function `fredr_request()` to run more general queries
against *any* [FRED API endpoint](https://research.stlouisfed.org/docs/api/fred/) (e.g. Categories,
Series, Sources, Releases, Tags).  The required parameter is `endpoint` (see `fredr_endpoints` for a list of valid endpoints) and then all API parameters are passed through as named arguments.  For example:

```{r fredr_request1}
fredr_request(endpoint = "tags/series", tag_names = "population;south africa", limit = 25L)
```

By default, `fredr_request()` will return a `tibble`.  Set `to_frame` to `FALSE` to return a generic `response` object from a `httr::GET()` request that can be further parsed with `httr::content()`:

```{r fredr_request2}
library(httr)
fredr_request(
  endpoint = "series/observations",
  series_id = "UNRATE",
  to_frame = FALSE
)
```

