---
title: "FRED Series"
author: "Sam Boysel"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{FRED Series}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  eval = !(Sys.getenv("FRED_API_KEY") == ""),
  cache = TRUE,
  collapse = TRUE,
  comment = "#>"
)
library(fredr)
options(digits = 4)
```

# Introduction

This vignette is intended to introduce the user to `fredr` functions for the [Series
endpoint](https://research.stlouisfed.org/docs/api/fred/#Series) of the FRED API.

FRED series are the primary data objects in the FRED database, each with string identifier.  For example:

- Civilian Unemployment Rate (`series_id = "UNRATE"`)
- Real Gross National Product (`series_id = "GNPCA"`)
- Effective Federal Funds Rate (`series_id = "FEDFUNDS"`)

FRED series are assigned categories and tags attributes for organization and classification.  The following examples illustrate the Series endpoint functions implements in `fredr`.

## Retrieve observations

The function `fredr()`, an alias for `fredr_series_observations()`, is the core function in `fredr` for fetching FRED data series.  See the [Get started](http://sboysel.github.io/fredr/articles/fredr.html) article and `fredr()` for usage examples.

## Search for FRED series

Use `fredr_series_search_text()` to search for a series _by text_ in the series description.  For example:

```{r fredr_series_search_text1}
fredr_series_search_text(
  search_text = "unemployment",
  limit = 100L
)
```

Use `fredr_series_search_id()` to search for a series _by integer ID_ of the series.  For example:

```{r fredr_search_id1}
fredr_series_search_id(
  search_text = "UNRATE",
  limit = 100L
)
```

## Search for FRED series by tags

Use `fredr_series_search_tags()` to search for series tags

```{r fredr_series_search_tags, message=FALSE, warning=FALSE}
fredr_series_search_tags(
  series_search_text = "unemployment",
  limit = 100L
)
```

## Search for FRED series by related tags

Use `fredr_search_related_tags()` to search for series tags related to a given tag.  For example, to search for tags related to the tag "usa" in which the series text matches "gnp", use the following:

```{r fredr_search_related_tags1}
fredr_series_search_related_tags(
  series_search_text = "gnp",
  tag_names = "usa",
  limit = 30L
)
```

## Return basic information for a FRED series

See `fredr_series()` for additional details.

## Return the categories for a FRED series

See `fredr_series_categories()` for additional details.

## Return the release for a FRED series

See `fredr_series_release()` for additional details.

## Return the tags for a FRED series

See `fredr_series_tags()` for additional details

## Return a set of recently updated FRED series

See `fredr_series_updates()` for additional details.

## Get the data vintage dates for a FRED series

See `fredr_series_vintagedates()` for additiional details

