---
title: "Using fredr"
author: "Sam Boysel"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Using fredr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  eval = !(Sys.getenv("FRED_API_KEY") == ""),
  cache = TRUE,
  collapse = TRUE,
  comment = "#>"
)
library(fredr)
options(digits = 4)
```

# Introduction

`fredr` interacts with the [Federal Reserve Economic
Data (FRED)](https://research.stlouisfed.org/fred2/) RESTful API, provided by the Federal
Reserve Bank of St. Louis.  Essentially a simple wrapper of
[`httr`](https://github.com/r-lib/httr) and the FRED API itself, `fredr` is
designed with simplicity and flexibility in mind.  The core functions are

- `fredr_set_key()` - Set the required FRED API key for the session.
- `fredr_series_observations()` - Fetch a FRED series.
- `fredr_series_search_text()` - Search for a FRED series by text.
- `fredr()` - Send a general request to the FRED API.

Objects are returned as `tibbles`.  The user is strongly encouraged to read the 
full [FRED API](https://research.stlouisfed.org/docs/api/fred/) documentation to 
leverage the full power of `fredr` and the FRED API.

## Installation

Currently, `fredr` is only available from GithHub.  You can install using `devtools::install_github`:

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("sboysel/fredr")
```

Load package

```{r fredr_load, eval=FALSE}
library(fredr)
```

## Authentication

To use `fredr` and the FRED API in general, you must first [obtain a FRED API
key](https://research.stlouisfed.org/docs/api/api_key.html).  It is also
recommended to reveiw the [FRED API Terms of
Use](https://research.stlouisfed.org/docs/api/terms_of_use.html).  Once you've obtained an API key, you can set the key as an environment variable using `fredr_set_key`

```{r fredr_set_key, eval=FALSE}
fredr_set_key("abcdefghijklmnopqrstuvwxyz123456")
```

where "abcdefghijklmnopqrstuvwxyz123456" is replaced with the actual key you obtain from FRED.  This will set the key for the current session.  You can persistently set the key by appending the line `FRED_API_KEY=abcdefghijklmnopqrstuvwxyz123456` to an `.Renviron` file in the working directory.  This can be done using a text editor or by running `usethis::edit_r_environ`.  If you edit the `.Renviron` file, remember to either restart the session or run `readRenviron(".Renviron")` for the changes to take effect. 

## Series

### Retrieve series

`fredr_series_observations` retrieves series observations (i.e. the actual time series data) for a specified FRED series ID.  The function returns a `tibble` with 2 columns (observation date and value).

```{r fredr_series_observations, message=FALSE, warning=FALSE}
fredr_series_observations(
  series_id = "UNRATE",
  observation_start = as.Date("1990-01-01")
)
```

Leverage the native features of the FRED API by passing additional parameters:

```{r fredr_series_observations2, message=FALSE, warning=FALSE}
fredr_series_observations(
  series_id = "UNRATE",
  observation_start = as.Date("1990-01-01"),
  frequency = "q",
  units = "chg"
)
```

`fredr` plays nicely with the [tidyverse](https://www.tidyverse.org/):

```{r fredr_series_observations3, message=FALSE, warning=FALSE}
library(tidyverse)
fredr_series_search_text(
  search_text = "federal funds",
  order_by = "popularity",
  sort_order = "desc",
  limit = 1) %>%
  pull(id) %>%
  fredr_series_observations(series_id = .) %>%
  ggplot(data = ., mapping = aes(x = date, y = FEDFUNDS)) +
    geom_line()
```

It is relatively straightforward to convert `tibbles` returned by `fredr` into other time series objects.  For example,

```{r fredr_series_observations4, message=FALSE, warning=FALSE}
library(xts)
gnpca <- fredr_series_observations(series_id = "GNPCA", units = "log") %>%
  mutate(GNPCA = GNPCA - lag(GNPCA)) %>%
  filter(!is.na(GNPCA))

gnpca_xts <- xts::xts(
  x = gnpca$GNPCA,
  order.by = gnpca$date
)

gnpca_xts %>%
  StructTS() %>%
  residuals() %>%
  acf(., main = "ACF for First Differenced real US GNP, log")
```

### Search for a series

Search for FRED series.

- Use `fredr_search` to search for a series by text in the series description
    ```{r fredr_search, message=FALSE, warning=FALSE}
    fredr_series_search_text("unemployment", limit = 100L)
    ```
- Use `fredr_search_id` to search for a series by the ID of the series
    ```{r fredr_search_id, message=FALSE, warning=FALSE}
    fredr_series_search_id("UNRATE", limit = 100L)
    ```
- Use `fredr_search_tags` to search for series tags
    ```{r fredr_search_tags, message=FALSE, warning=FALSE}
    fredr_series_search_tags("unemployment", limit = 100L)
    ```
- Use `fredr_search_rel_tags` to search for series tags related to a given tag.  For example, to search for tags related to the tag "usa" in which the series text matches "gnp", use the following:
    ```{r fredr_search_rel_tags, message=FALSE, warning=FALSE}
    fredr_series_search_related_tags("gnp", "usa", limit = 30L)
    ```
    
See `help(fredr_search)` for more details.

## Tags

Series tags can be listed or searched for using `fredr_tags`.  For tags matched by the specific request, returned objects will include information such as tag description, popularity, and the number of associated series.  The following examples show how to use the various parameters of `fredr_tags` to 

- To list all tags, run `fredr_tags` without any parameters (note that the parameter `limit` defaults to 1000)
    ```{r fredr_tags1, message=FALSE, warning=FALSE}
    fredr_tags()
    ```
- Return specific tags by tag name.  You can specify multiple tags in a single string by delimiting with a semicolon:
    ```{r fredr_tags2, message=FALSE, warning=FALSE}
    fredr_tags(tag_names = "gdp;oecd")
    ```
- Return tags for a given group ID
    ```{r fredr_tags3, message=FALSE, warning=FALSE}
    fredr_tags(tag_group_id = "geo", limit = 50L)
    ```
- Search for tags by text
    ```{r fredr_tags4, message=FALSE, warning=FALSE}
    fredr_tags(search_text = "unemployment")
    ```

## View FRED API documentation

To get the most out of the native features of the FRED API, it is highly recommended to review the [API endpoint documentation](https://research.stlouisfed.org/docs/api/fred/). Within an R session, you can quickly access the web documentation for any endpoint with the convenience function `fredr_docs`.  The following example will open a web browser to the FRED API documentation page on `series/observation` endpoint.
```{r fredr_docs, message=FALSE, warning=FALSE, eval=FALSE}
fredr_docs(endpoint = "series/observations")
```

You may also use the `params` option for `fredr_docs` to go straight to the
endpoint's Parameters section.
```{r fredr_docs2, message=FALSE, warning=FALSE, eval=FALSE}
fredr_docs(endpoint = "category/related_tags", params = TRUE)
```

`fredr` is packaged with a list of possible endpoints in the data frame `fredr_endpoints`
```{r fredr_docs3, message=FALSE, warning=FALSE, width = 180}
fredr_endpoints
```

## General queries

You can also use the low-level function `fredr` to run more general queries
against *any* [FRED API
endpoint](https://research.stlouisfed.org/docs/api/fred/) (e.g. Categories,
Series, Sources, Releases, Tags).  This is also useful to run complex queries or .
```{r fredr_general}
fredr_request(endpoint = "tags/series", tag_names = "population;south africa")
```

By default, `fredr` (and therefore all `fredr_*` functions) return a `tibble`.  Set `to_frame` to `FALSE` to return a generic `response` object from a `httr::GET` request that can be further parsed with `httr::content`
```{r fredr_general2}
library(httr)
resp <- fredr_request(endpoint = "series/observations", series_id = "UNRATE", to_frame = FALSE)
resp
```

